% !TeX root = principal.tex
\documentclass{article}

\usepackage[brazil]{babel}
\usepackage[dvips]{epsfig}
\usepackage{graphicx,color}

\usepackage{lscape, rotating}
\usepackage{varioref,float,amssymb,amsmath}
\usepackage{float,amsfonts,amsthm}
\usepackage{changebar,longtable}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{makeidx}
%\makeindex

%\usepackage{draftcopy}
\usepackage{subfigure}
%\draftcopySetGrey{.98}
\newcommand{\B}{{\tt\symbol{92}}}
\newcommand{\til}{{\tt\symbol{126}}}
\newcommand{\chap}{{\tt\symbol{94}}}
\newcommand{\agud}{{\tt\symbol{13}}}
\newcommand{\crav}{{\tt\symbol{18}}}
\newcommand{\cat}[3]{#1 \stackrel{#2}{\mathbf{\sqcap}}#3}

\newtheorem{lema}{Lema}%[section]
\newtheorem{teore}{Teorema}%[section]
\newtheorem{defi}{Definição}%[section]
\newtheorem{corol}{Corolário}%[section]
\newtheorem{ex}{Exemplo}%[section]
\newtheorem{propri}{Propriedade}%[section]
\newcommand{\dem}{\noindent \underline{Demonstração}: $\,$}
\newcommand{\fim}{\hfill $\rule{2.0mm}{2.0mm}$ \\}    % marcação de fim das demonstrações

%\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

\newtheorem{obs}{Observa\c{c}\~ao}%[section]
\newcommand{\preca}{pre\-con\-di\-ci\-o\-na\-da}
\newcommand{\preco}{pre\-con\-di\-ci\-o\-na\-do}
\newcommand{\precor}{pre\-con\-di\-ci\-o\-na\-dor}
\newcommand{\precors}{pre\-con\-di\-ci\-o\-na\-do\-res}
\newcommand{\bibdirec}{C:}
\newcommand{\range}[1]{\ensuremath{\operatorname{Im}(#1)}}
\newcommand{\Ker}[1]{\ensuremath{\operatorname{Nuc}(#1)}}
\newcommand{\dime}[1]{\ensuremath{\operatorname{dim}(#1)}}
\newcommand{\norma}[1]{\ensuremath{{\Vert #1\Vert}}}
\newcommand{\gera}[1]{\ensuremath{{\langle #1\rangle}}}
\newcommand{\bml}{\ensuremath{\mathbf{b}}}
\newcommand{\xml}{\ensuremath{\mathbf{x}}}
\newcommand{\yml}{\ensuremath{\mathbf{y}}}
\newcommand{\rml}{\ensuremath{\mathbf{r}}}
\newcommand{\hml}{\ensuremath{\mathbf{h}}}
\newcommand{\bbox}{\ensuremath{\mathcal{B}_n^{\Box}}}
\newcommand{\bboxo}{\ensuremath{\mathcal{\overline{B}}_n^{\Box}}}

%\newcommand{\versao}[2]{\ifthenelse{\boolean{versaocnmac}}{#1}{#2}}
\newcommand{\oblq}{%
 \ensuremath{%
   \mathrel{%
     \raisebox{-2.7pt}{$\scriptstyle-$}%
     \hspace{-4.5pt}%
     \raisebox{0.1pt}{$\scriptscriptstyle\not$}%
     \hspace{5.5pt}}}}

\newcounter{exernum}\setcounter{exernum}{0}
\newcounter{totexernum}
\newcounter{equaux}%for numbering equations
%introducao dos pacotes abaixo

\usepackage{calc}
\usepackage{subfigure}
\usepackage{ifthen}

\renewcommand\theequation{\arabic{equation}}

\usepackage{float}
\floatstyle{ruled}
\newfloat{algor}{thp}{loa}%[section]
\floatname{algor}{Algoritmo}

%\setlength{\parindent}{1em} % Change the value as needed
% fim de introdução de novos pacotes

\title{Arnoldi, FOM e GMRES}
\author{ Luiz Mariano  Carvalho }

\date{\today
}

\begin{document}
	
\maketitle

\input{gmres}



% Referências Bibliográficas - Obrigatório

\markboth{}{Bibliografia}

\begin{thebibliography}{100}
	
    \bibitem{Arnoldi51principle} W.~E. Arnoldi. \newblock The principle of minimized iterations in the solution of the
    matrix
  eigenvalue problem.
\newblock {\em Quart. of Appl. Math.}, 9(1):17--29, 1951.

    \bibitem{Brezinski2002Outils} C.~Brezinski. \newblock {\em Outils d'analyse numérique pour l'automatique},
    chapter
  Résolution des systèmes linéaires, pages 109--144.
\newblock Hermes Science Publications, 2002.


\bibitem{Chaitin-ChatelinFraysse1996Lectures} F.~{Chaitin-Chatelin} and V.~Frayssé. \newblock {\em Lectures on
    Finite Precision Computations}. \newblock SIAM, Philadelphia, 1996.

\bibitem{Embree1999How} M.~Embree. \newblock How descriptive are {GMRES} convergence bounds? \newblock Technical
report, Oxford University Computing Laboratory, 1999.

	
    \bibitem{Greenbaum97Iterative} A.~Greenbaum. \newblock {\em Iterative Methods for Solving Linear Systems}.
    \newblock SIAM, Philadelphia, 1997.
	
	\bibitem{GreenbaumPtakEtAl96Any} A.~Greenbaum, V.~Pták, and Z.~Strako{\u{s}}. \newblock Any nonincreasing
	convergence curve is possible for {GMRES}. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
	17(3):465--469, July 1996.
	

		
	



	

    \bibitem{Meurant1999Computer} G.~Meurant. \newblock {\em Computer solution of large linear systems}. \newblock
    North-Holland, 1999.

	
	\bibitem{Meyer00Matrix} C.~D. Meyer. \newblock {\em Matrix analysis and applied liner algebra}. \newblock SIAM,
	2000.
	
\bibitem{Morgan95Restarted} R.~B. Morgan. \newblock A restarted {GMRES} method augmented with eigenvectors.
    \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  16(4):1154--1171, 1995.


\bibitem{Morgan00Implicitly} R.~B. Morgan. \newblock Implicitly restarted {GMRES} and {Arnoldi} methods for
nonsymmetric
systems of equations.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
21(4):1112--1135, 2000.





\bibitem{NachtigalReddyEtAl1992How} N.~M. Nachtigal, S.~C. Reddy, and L.~N. Trefethen. \newblock How fast are
    nonsymmetric matrix iterations? \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  13(3):778--795, 1992.

  \bibitem{PaigeParlettEtAl95Approximate} C.~C. Paige, B.~N. Parlett, and H.~A. van~der Vorst. \newblock Approximate
  solutions and eigenvalue bounds from {Krylov} subspaces. \newblock {\em Numerical Linear Algebra with
  Applications}, 2(2):115 -- 133,
1995.

\bibitem{PaigeRozloznikEtAl2006MODIFIED} C.~C. Paige, M.~Rozlo{\u{z}}n{\'{\i}}k, and Z.~Strako{\u{s}}. \newblock
  Modified {G}ram-{S}chmidt ({MGS}), least squares, and backward
stability of {MGS-GMRES}.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
28(1):264--284, 2006.

\bibitem{Rozloznik1997Numerical} M.~Rozlo\u{z}ník. \newblock {\em Numerical Stability of the GMRES Method}.
    \newblock PhD thesis, Institute of Computer Science, Academy of Sciences of the
  Czech Republic, Prague, April 1997.


\bibitem{Saad1981Krylov} Y.~Saad. \newblock {Krylov} subspace methods for solving large unsymmetric linear
  systems.
\newblock {\em Math. Comp.}, 37(155):105--126, July 1981.

	\bibitem{Saad03Iterative} Y.~Saad. \newblock {\em Iterative Methods for Sparse Linear Systems}. \newblock SIAM,
	2nd edition, 2003.
	
	\bibitem{SaadSchultz86GMRES} Y.~Saad and M.~H. Schultz. \newblock {GMRES}: a generalized minimal residual
    algorithm for solving
  nonsymmetric linear systems.

  \bibitem{SaadVorst00Iterative} Y.~Saad and H.~A. van~der Vorst. \newblock Iterative solution of linear systems in
    the 20th century. \newblock {\em Journal of Computational and Applied Mathematics},
  123(1-2):1--23, 2000.


    \bibitem{Simoncini00Convergence} V.~Simoncini. \newblock On the convergence of restarted {Krylov} subspace
    methods. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  22(2):430--452, 2000.

 
    \bibitem{SimonciniSzyld2007Recent} V.~Simoncini and D.~B. Szyld. \newblock Recent computational developments in
    {Krylov} subspace methods for
  linear systems.
\newblock {\em Numerical Linear Algebra with Applications}, 14:1 -- 59, 2007.

	
    \bibitem{Stewart1973Introduction} G.~W. Stewart. \newblock {\em Introduction to Matrix Computations}. \newblock
    Academic Press, New York, 1973.

    \bibitem{Stewart98Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume I}: Basic Algorithms}.
    \newblock SIAM, Philadelphia, PA, USA, 1998.


	\bibitem{Stewart01Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume II}: Eigensystems}. \newblock
	SIAM, 2001.
	
	\bibitem{Trefethen1990Algorithms} L.~N. Trefethen. \newblock {\em Algorithms for Approximation II}, chapter
    Approximation theory
  and numerical linear algebra, pages 336--360.
\newblock Chapman and Hall, London, 1990.


	
	
\bibitem{Vorst03Iterative} H.~van~der Vorst. \newblock {\em Iterative {Krylov} Methods for Large Linear systems}.
\newblock Cambridge University Press, Cambridge, April 2003.
	
	

	

\bibitem{Zemke2003Krylov} J.-P.~M. Zemke. \newblock {\em {Krylov} Subspace Methods in Finite Precision: A Unified
Approach}.
\newblock PhD thesis, Technischen Universität Hamburg-Harburg, 2003.
	
	
\bibitem{Zou2023}  Qinmeng Zou.
\newblock  {GMRES} algorithms over 35 years,
   \newblock{\em Applied Mathematics and Computation},
 2023.
		



	
	
	\markboth{}{}
	
\end{thebibliography}






\end{document}
