
\markboth{}{Bibliografia}

\begin{thebibliography}{100}
	
    \bibitem{Arnoldi51principle} W.~E. Arnoldi. \newblock The principle of minimized iterations in the solution of the
    matrix
  eigenvalue problem.
\newblock {\em Quart. of Appl. Math.}, 9(1):17--29, 1951.


	\bibitem{BaiDemmelEtAl2000Templates} Z.~Bai, J.~Demmel, J.~Dongarra, A.~Ruhe, and H.~van~der Vorst, editors.
	\newblock {\em Templates for the solution of Algebraic Eigenvalue Problems: A
		Practical Guide}.
	\newblock SIAM, Philadelphia, 2000.


	\bibitem{Beattie1998Harmonic} C.~Beattie. \newblock Harmonic {R}itz and {L}ehman bounds. \newblock {\em ETNA},
	7:18--39, 1998.

	\bibitem{Brezinski2002Outils} C.~Brezinski. \newblock {\em Outils d'analyse numérique pour l'automatique},
    chapter
  Résolution des systèmes linéaires, pages 109--144.
\newblock Hermes Science Publications, 2002.

\bibitem{Chaitin-ChatelinFraysse1996Lectures} F.~{Chaitin-Chatelin} and V.~Frayssé. \newblock {\em Lectures on
    Finite Precision Computations}. \newblock SIAM, Philadelphia, 1996.



	\bibitem{Cullum1996Iterative} J.~K. Cullum. \newblock Iterative methods for solving ${A}x=b$ {GMRES-FOM} versus
	{QMR/BiCG}. \newblock Technical Report TR-96-2, Institute for Advances Studies, University
	of Maryland, 1996.
	
	\bibitem{Embree1999How} M.~Embree. \newblock How descriptive are {GMRES} convergence bounds? \newblock Technical
report, Oxford University Computing Laboratory, 1999.

	\bibitem{GoossensRoose99Ritz} S.~Goossens and D.~Roose. \newblock {Ritz} and harmonic {Ritz} values and the
	convergence of {FOM} and
	{GMRES}.
	\newblock {\em Numerical linear algebra with applications}, 6(4):281--293,
	1999.
	
	\bibitem{Greenbaum97Iterative} A.~Greenbaum. \newblock {\em Iterative Methods for Solving Linear Systems}.
    \newblock SIAM, Philadelphia, 1997.
	
	
	\bibitem{GreenbaumPtakEtAl96Any} A.~Greenbaum, V.~Pták, and Z.~Strako{\u{s}}. \newblock Any nonincreasing
	convergence curve is possible for {GMRES}. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
	17(3):465--469, July 1996.
	

	

	
	\bibitem{HornJohnson1985} R.A.~Horn and C.R~Johnson. \newblock {\em Matrix Analysis}. \newblock
	Cambridge University Press, 1985.
  
  
	

		
	\bibitem{HornJohnson87Matrix} R.~A. Horn and C.~R. Johnson. \newblock {\em Matrix Analysis}. \newblock Cambridge
	University Press, 1987.
	


	
	\bibitem{JiaStewart2001analysis} Z.~Jia and G.~W. Stewart. \newblock An analysis of the {Rayleigh-Ritz} method for
	approximating
	eigenspaces.
	\newblock {\em Mathematics of Computation}, 70(234):637--647, 2001.
	
	\bibitem{Meurant1999Computer} G.~Meurant. \newblock {\em Computer solution of large linear systems}. \newblock
    North-Holland, 1999.

    \bibitem{Meurant2020Krylov}  G.~Meurant and J.D.~Tebbens.
    \newblock{\em Krylov Methods for Nonsymmetric Linear Systems}, Springer, 2020.
	

	

	
	\bibitem{Meyer00Matrix} C.~D. Meyer. \newblock {\em Matrix analysis and applied liner algebra}. \newblock SIAM,
	2000.
	
\bibitem{Morgan1991Computing} R.~B. Morgan. \newblock Computing interior eigenvalues of large matrices. \newblock
{\em Lin. Alg. and Its Applic.}, 154/156:289--309, 1991.

\bibitem{Morgan95Restarted} R.~B. Morgan. \newblock A restarted {GMRES} method augmented with eigenvectors.
    \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  16(4):1154--1171, 1995.


\bibitem{Morgan00Implicitly} R.~B. Morgan. \newblock Implicitly restarted {GMRES} and {Arnoldi} methods for
nonsymmetric
systems of equations.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
21(4):1112--1135, 2000.
	
\bibitem{NachtigalReddyEtAl1992How} N.~M. Nachtigal, S.~C. Reddy, and L.~N. Trefethen. \newblock How fast are
    nonsymmetric matrix iterations? \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  13(3):778--795, 1992.

  \bibitem{PaigeParlettEtAl95Approximate} C.~C. Paige, B.~N. Parlett, and H.~A. van~der Vorst. \newblock Approximate
  solutions and eigenvalue bounds from {Krylov} subspaces. \newblock {\em Numerical Linear Algebra with
  Applications}, 2(2):115 -- 133,
1995.

\bibitem{PaigeRozloznikEtAl2006MODIFIED} C.~C. Paige, M.~Rozlo{\u{z}}n{\'{\i}}k, and Z.~Strako{\u{s}}. \newblock
  Modified {G}ram-{S}chmidt ({MGS}), least squares, and backward
stability of {MGS-GMRES}.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
28(1):264--284, 2006.


	
	\bibitem{Parlett1998symmetric} B.~N. Parlett. \newblock {\em The symmetric eigenvalue problem}. \newblock SIAM,
	Philadelphia, 1998. \newblock Corrected reprint of the 1980 original.

\bibitem{Rozloznik1997Numerical} M.~Rozlo\u{z}ník. \newblock {\em Numerical Stability of the GMRES Method}.
    \newblock PhD thesis, Institute of Computer Science, Academy of Sciences of the
  Czech Republic, Prague, April 1997.


\bibitem{Saad1981Krylov} Y.~Saad. \newblock {Krylov} subspace methods for solving large unsymmetric linear
  systems.
\newblock {\em Math. Comp.}, 37(155):105--126, July 1981.

	\bibitem{Saad03Iterative} Y.~Saad. \newblock {\em Iterative Methods for Sparse Linear Systems}. \newblock SIAM,
	2nd edition, 2003.
	
	\bibitem{SaadSchultz86GMRES} Y.~Saad and M.~H. Schultz. \newblock {GMRES}: a generalized minimal residual
    algorithm for solving
  nonsymmetric linear systems.

  \bibitem{SaadVorst00Iterative} Y.~Saad and H.~A. van~der Vorst. \newblock Iterative solution of linear systems in
    the 20th century. \newblock {\em Journal of Computational and Applied Mathematics},
  123(1-2):1--23, 2000.



	
	\bibitem{Scott1982Advantages} D.~S. Scott. \newblock The advantages of inverted operators in {Rayleigh--Ritz}
	approximations.
	\newblock {\em SIAM Journal on Scientific and Statistical Computing},
	3(1):68--75, 1982.
		
	\bibitem{Simoncini00Convergence} V.~Simoncini. \newblock On the convergence of restarted {Krylov} subspace
    methods. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  22(2):430--452, 2000.

 
    \bibitem{SimonciniSzyld2007Recent} V.~Simoncini and D.~B. Szyld. \newblock Recent computational developments in
    {Krylov} subspace methods for
  linear systems.
\newblock {\em Numerical Linear Algebra with Applications}, 14:1 -- 59, 2007.

		
	\bibitem{SleijpenEshof2003use} G.~L.~G. Sleijpen and J.~van~den Eshof. \newblock On the use of harmonic {Ritz}
	pairs in approximating internal
	eigenpairs.
	\newblock {\em Linear Algebra and its Applications}, 358(1-3):115--137, January
	2003.
	
	\bibitem{SleijpenVorst00JacobiDavidson} G.~L.~G. Sleijpen and H.~A. van~der Vorst. \newblock A {Jacobi--Davidson}
	iteration method for linear eigenvalue problems. \newblock {\em SIAM Review}, 42(2):267--293, 2000. \newblock
	This paper originally appeared in SIAM Journal on Matrix Analysis and
	Applications, Volume 17, Number 2, 1996, pages 401-425.
	

	\bibitem{Stewart1973Introduction} G.~W. Stewart. \newblock {\em Introduction to Matrix Computations}. \newblock
    Academic Press, New York, 1973.

    \bibitem{Stewart98Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume I}: Basic Algorithms}.
    \newblock SIAM, Philadelphia, PA, USA, 1998.


	
	\bibitem{Stewart01Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume II}: Eigensystems}. \newblock
	SIAM, 2001.
	
	
	\bibitem{Trefethen1990Algorithms} L.~N. Trefethen. \newblock {\em Algorithms for Approximation II}, chapter
    Approximation theory
  and numerical linear algebra, pages 336--360.
\newblock Chapman and Hall, London, 1990.


	
	
\bibitem{Vorst03Iterative} H.~van~der Vorst. \newblock {\em Iterative {Krylov} Methods for Large Linear systems}.
\newblock Cambridge University Press, Cambridge, April 2003.
	
	
\bibitem{Zemke2003Krylov} J.-P.~M. Zemke. \newblock {\em {Krylov} Subspace Methods in Finite Precision: A Unified
Approach}.
\newblock PhD thesis, Technischen Universität Hamburg-Harburg, 2003.
	
	
\bibitem{Zou2023}  Q. Zou.
\newblock  {GMRES} algorithms over 35 years,
   \newblock{\em Applied Mathematics and Computation},
 2023.
			

	
	
	\markboth{}{}
	
\end{thebibliography}

