% !TeX root = principal.tex
\documentclass{article}

\usepackage[brazil]{babel}
\usepackage[dvips]{epsfig}
\usepackage{graphicx,color}

\usepackage{lscape, rotating}
\usepackage{varioref,float,amssymb,amsmath}
\usepackage{float,amsfonts,amsthm}
\usepackage{changebar,longtable}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{makeidx}
%\makeindex

%\usepackage{draftcopy}
\usepackage{subfigure}
%\draftcopySetGrey{.98}
\newcommand{\B}{{\tt\symbol{92}}}
\newcommand{\til}{{\tt\symbol{126}}}
\newcommand{\chap}{{\tt\symbol{94}}}
\newcommand{\agud}{{\tt\symbol{13}}}
\newcommand{\crav}{{\tt\symbol{18}}}
\newcommand{\cat}[3]{#1 \stackrel{#2}{\mathbf{\sqcap}}#3}

\newtheorem{lema}{Lema}%[section]
\newtheorem{teore}{Teorema}%[section]
\newtheorem{defi}{Definição}%[section]
\newtheorem{corol}{Corolário}%[section]
\newtheorem{ex}{Exemplo}%[section]
\newtheorem{propri}{Propriedade}%[section]
\newcommand{\dem}{\noindent \underline{Demonstração}: $\,$}
\newcommand{\fim}{\hfill $\rule{2.0mm}{2.0mm}$ \\}    % marcação de fim das demonstrações

%\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}

\newtheorem{obs}{Observa\c{c}\~ao}%[section]
\newcommand{\preca}{pre\-con\-di\-ci\-o\-na\-da}
\newcommand{\preco}{pre\-con\-di\-ci\-o\-na\-do}
\newcommand{\precor}{pre\-con\-di\-ci\-o\-na\-dor}
\newcommand{\precors}{pre\-con\-di\-ci\-o\-na\-do\-res}
\newcommand{\bibdirec}{C:}
\newcommand{\range}[1]{\ensuremath{\operatorname{Im}(#1)}}
\newcommand{\Ker}[1]{\ensuremath{\operatorname{Nuc}(#1)}}
\newcommand{\dime}[1]{\ensuremath{\operatorname{dim}(#1)}}
\newcommand{\norma}[1]{\ensuremath{{\Vert #1\Vert}}}
\newcommand{\gera}[1]{\ensuremath{{\langle #1\rangle}}}
\newcommand{\bml}{\ensuremath{\mathbf{b}}}
\newcommand{\xml}{\ensuremath{\mathbf{x}}}
\newcommand{\yml}{\ensuremath{\mathbf{y}}}
\newcommand{\rml}{\ensuremath{\mathbf{r}}}
\newcommand{\hml}{\ensuremath{\mathbf{h}}}
\newcommand{\bbox}{\ensuremath{\mathcal{B}_n^{\Box}}}
\newcommand{\bboxo}{\ensuremath{\mathcal{\overline{B}}_n^{\Box}}}

%\newcommand{\versao}[2]{\ifthenelse{\boolean{versaocnmac}}{#1}{#2}}
\newcommand{\oblq}{%
 \ensuremath{%
   \mathrel{%
     \raisebox{-2.7pt}{$\scriptstyle-$}%
     \hspace{-4.5pt}%
     \raisebox{0.1pt}{$\scriptscriptstyle\not$}%
     \hspace{5.5pt}}}}

\newcounter{exernum}\setcounter{exernum}{0}
\newcounter{totexernum}
\newcounter{equaux}%for numbering equations
%introducao dos pacotes abaixo

\usepackage{calc}
\usepackage{subfigure}
\usepackage{ifthen}

\renewcommand\theequation{\arabic{equation}}

\usepackage{float}
\floatstyle{ruled}
\newfloat{algor}{thp}{loa}%[section]
\floatname{algor}{Algoritmo}

%\setlength{\parindent}{1em} % Change the value as needed
% fim de introdução de novos pacotes

\title{Pares de Ritz e Pares Harmônicos de Ritz}
\author{ Luiz Mariano  Carvalho }

\date{\today
}

\begin{document}
	
\maketitle

\input{ritz}



% Referências Bibliográficas - Obrigatório

\markboth{}{Bibliografia}

\begin{thebibliography}{100}
	
	\bibitem{BaiDemmelEtAl2000Templates} Z.~Bai, J.~Demmel, J.~Dongarra, A.~Ruhe, and H.~van~der Vorst, editors.
	\newblock {\em Templates for the solution of Algebraic Eigenvalue Problems: A
		Practical Guide}.
	\newblock SIAM, Philadelphia, 2000.
	\bibitem{Beattie1998Harmonic} C.~Beattie. \newblock Harmonic {R}itz and {L}ehman bounds. \newblock {\em ETNA},
	7:18--39, 1998.

	\bibitem{Cullum1996Iterative} J.~K. Cullum. \newblock Iterative methods for solving ${A}x=b$ {GMRES-FOM} versus
	{QMR/BiCG}. \newblock Technical Report TR-96-2, Institute for Advances Studies, University
	of Maryland, 1996.
	
	
	\bibitem{GoossensRoose99Ritz} S.~Goossens and D.~Roose. \newblock {Ritz} and harmonic {Ritz} values and the
	convergence of {FOM} and
	{GMRES}.
	\newblock {\em Numerical linear algebra with applications}, 6(4):281--293,
	1999.
	

	
	\bibitem{GreenbaumPtakEtAl96Any} A.~Greenbaum, V.~Pták, and Z.~Strako{\u{s}}. \newblock Any nonincreasing
	convergence curve is possible for {GMRES}. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
	17(3):465--469, July 1996.
	

	

	

	

		
	\bibitem{HornJohnson87Matrix} R.~A. Horn and C.~R. Johnson. \newblock {\em Matrix Analysis}. \newblock Cambridge
	University Press, 1987.
	


	
	\bibitem{JiaStewart2001analysis} Z.~Jia and G.~W. Stewart. \newblock An analysis of the {Rayleigh-Ritz} method for
	approximating
	eigenspaces.
	\newblock {\em Mathematics of Computation}, 70(234):637--647, 2001.
	

	

	
	\bibitem{Meyer00Matrix} C.~D. Meyer. \newblock {\em Matrix analysis and applied liner algebra}. \newblock SIAM,
	2000.
	
\bibitem{Morgan1991Computing} R.~B. Morgan. \newblock Computing interior eigenvalues of large matrices. \newblock
{\em Lin. Alg. and Its Applic.}, 154/156:289--309, 1991.
	
\bibitem{Morgan00Implicitly} R.~B. Morgan. \newblock Implicitly restarted {GMRES} and {Arnoldi} methods for
nonsymmetric
systems of equations.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
21(4):1112--1135, 2000.
	

	
	\bibitem{Parlett1998symmetric} B.~N. Parlett. \newblock {\em The symmetric eigenvalue problem}. \newblock SIAM,
	Philadelphia, 1998. \newblock Corrected reprint of the 1980 original.

\bibitem{PaigeParlettEtAl95Approximate} C.~C. Paige, B.~N. Parlett, and H.~A. van~der Vorst. \newblock Approximate
solutions and eigenvalue bounds from {Krylov} subspaces. \newblock {\em Numerical Linear Algebra with
	Applications}, 2(2):115 -- 133,
1995.
	
	\bibitem{Saad03Iterative} Y.~Saad. \newblock {\em Iterative Methods for Sparse Linear Systems}. \newblock SIAM,
	2nd edition, 2003.
	
	
	\bibitem{Scott1982Advantages} D.~S. Scott. \newblock The advantages of inverted operators in {Rayleigh--Ritz}
	approximations.
	\newblock {\em SIAM Journal on Scientific and Statistical Computing},
	3(1):68--75, 1982.
		
	
	\bibitem{SleijpenEshof2003use} G.~L.~G. Sleijpen and J.~van~den Eshof. \newblock On the use of harmonic {Ritz}
	pairs in approximating internal
	eigenpairs.
	\newblock {\em Linear Algebra and its Applications}, 358(1-3):115--137, January
	2003.
	
	\bibitem{SleijpenVorst00JacobiDavidson} G.~L.~G. Sleijpen and H.~A. van~der Vorst. \newblock A {Jacobi--Davidson}
	iteration method for linear eigenvalue problems. \newblock {\em SIAM Review}, 42(2):267--293, 2000. \newblock
	This paper originally appeared in SIAM Journal on Matrix Analysis and
	Applications, Volume 17, Number 2, 1996, pages 401-425.
	

	

	
	\bibitem{Stewart01Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume II}: Eigensystems}. \newblock
	SIAM, 2001.
	
	
	
	
	
	

	

	
	
	

	

	

	

	

	

	
	
	\markboth{}{}
	
\end{thebibliography}






\end{document}
