% Referências Bibliográficas - Obrigatório

\markboth{}{Bibliografia}

\begin{thebibliography}{100}

\bibitem{AllaireKaber2008Numerical} G.~Allaire and S.~M. Kaber. \newblock {\em Numerical Linear Algebra}.
    \newblock Springer, 2008.

\bibitem{ArbenzChinellatoEtAl2006Software} P.~Arbenz, O.~Chinellato, M.~Sala, P.~Arbenz, and M.~H. Gutknecht.
    \newblock {\em Software for numerical linear algebra}. \newblock ETH, 2006.

\bibitem{ArioliDuffEtAl92Stopping} M.~Arioli, I.~Duff, and D.~Ruiz. \newblock Stopping criteria for iterative
    solvers. \newblock {\em SIAM J. Matrix Anal. Appl.}, 13(1):138--144, January 1992.

\bibitem{ArioliDuffEtAl07Note} M.~Arioli, I.~S. Duff, S.~Gratton, and S.~Pralet. \newblock A note on {GMRES}
    preconditioned by a perturbed {$L D L^T$}
  decomposition with static pivoting.
\newblock {\em SIAM Journal on Scientific Computing}, 29(5):2024--2044, 2007.

\bibitem{Arnoldi51principle} W.~E. Arnoldi. \newblock The principle of minimized iterations in the solution of the
    matrix
  eigenvalue problem.
\newblock {\em Quart. of Appl. Math.}, 9(1):17--29, 1951.

\bibitem{AxelssonVassilevski91Black} O.~Axelsson and P.~S. Vassilevski. \newblock A black box generalized
    conjugate gradient solver with inner
  iterations and variable-step preconditioning.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
  12(4):625--644, 1991.

\bibitem{BaglamaCalvettiEtAl1998Adaptively} J.~Baglama, D.~Calvetti, G.~H. Golub, and L.~Reichel. \newblock
    Adaptively preconditioned {GMRES} algorithms. \newblock {\em SIAM Journal on Scientific Computing},
    20(1):243--269, 1998.

\bibitem{BaiDemmelEtAl2000Templates} Z.~Bai, J.~Demmel, J.~Dongarra, A.~Ruhe, and H.~van~der Vorst, editors.
    \newblock {\em Templates for the solution of Algebraic Eigenvalue Problems: A
  Practical Guide}.
\newblock SIAM, Philadelphia, 2000.

\bibitem{BakerDennisEtAl06Improving} A.~H. Baker, J.~M. Dennis, and E.~R. Jessup. \newblock On improving linear
    solver performance: A block variant of {GMRES}. \newblock {\em SIAM Journal on Scientific Computing},
    27(5):1608--1626, 2006.

\bibitem{BalayBuschelmanEtAl05PETSc} S.~Balay, K.~Buschelman, V.~Eijkhout, W.~Gropp, D.~Kaushik, M.~Knepley,
    L.~C.
  McInnes, B.~Smith, and H.~Zhang.
\newblock {PETSc} user's manual. \newblock Technical Report ANL-95/11, Argonne National Laboratory, 2005.
\newblock Revision 2.3.0.

\bibitem{BarrettBerryEtAl94Templates} R.~Barrett, M.~Berry, T.~F. Chan, J.~Demmel, J.~Donato, J.~Dongarra,
  V.~Eijkhout, R.~Pozo, C.~Romine, and H.~van~der Vorst.
\newblock {\em Templates for the Solution of Linear Systems: Building Blocks
  for Iterative Methods}.
\newblock {SIAM} press, Philadelphia, 1994.

\bibitem{Beattie1998Harmonic} C.~Beattie. \newblock Harmonic {R}itz and {L}ehman bounds. \newblock {\em ETNA},
    7:18--39, 1998.

\bibitem{Benzi02Preconditioning} M.~Benzi. \newblock Preconditioning techniques for large linear systems: a
    survey. \newblock {\em Journal of Computational Physics}, 182(2):418--477, November
  2002.

\bibitem{BenziCullumEtAl00Robust} M.~Benzi, J.~K. Cullum, and M.~T{\accent 6u}ma. \newblock Robust approximate
    inverse preconditioning for the conjugate gradient
  method.
\newblock {\em SIAM Journal on Scientific Computing}, 22:1318--1332, 2000.

\bibitem{BenziKouhiaEtAl01Stabilized} M.~Benzi, R.~Kouhia, and M.~T{\accent 6u}ma. \newblock Stabilized and block
    approximate inverse preconditioners for problems
  in solid and structural mechanics.
\newblock {\em Computer methods in applied mechanics and engineering},
  190:6533--6554, 2001.

\bibitem{BenzMeyerEtAl96sparse} M.~Benzi, C.~D. Meyer, and M.~T{\accent 6u}ma. \newblock A sparse approximate
    inverse preconditioner for the conjugate
  gradient method.
\newblock {\em SIAM Journal on Scientific Computing}, 17:1135--1149., 1996.

\bibitem{BenziTuma99comparative} M.~Benzi and M.~T{\accent 6u}ma. \newblock A comparative study of sparse
    approximate inverse preconditioners. \newblock {\em Applied Numerical Mathematics}, 30:305--340, 1999.

%\bibitem{BischofHansen1991Structure-Preserving} C.~H. Bischof and P.~C. Hansen. \newblock Structure-preserving and
%    rank-revealing {QR}-factorizations. \newblock {\em SIAM Journal on Scientific and Statistical Computing},
%  12(6):1332--1350, 1991.
%
%\bibitem{BischofHansen1992block} C.~H. Bischof and P.~C. Hansen. \newblock A block algorithm for computing
%    rank-revealing {QR} factorizations. \newblock {\em Numer. Algorithms}, 2:371--391, 1992.

%\bibitem{BischofQuintana-Orti1998Computing} C.~H. Bischof and G.~Quintana-Ortí. \newblock Computing rank-revealing
%    {QR} factorizations of dense matrices. \newblock {\em ACM Trans. Math. Software}, 24:226--253, 1998.

\bibitem{BourasFraysse2000relaxationa} A.~Bouras and V.~Frayssé. \newblock A relaxation strategy for inexact
    matrix-vector products for {K}rylov
  methods.
\newblock {Technical Report} TR/PA/00/15, CERFACS, Toulouse, France, 2000. \newblock {Submitted to SIAM Journal in
Matrix Analysis and Applications}.

\bibitem{BourasFraysse2000relaxation} A.~Bouras and V.~Frayssé. \newblock A relaxation strategy for the {A}rnoldi
    method in eigenproblems. \newblock {Technical Report} TR/PA/00/16, CERFACS, Toulouse, France, 2000.

\bibitem{BourasFraysse2005Inexact} A.~Bouras and V.~Frayssé. \newblock Inexact matrix-vector products in {Krylov}
    methods for solving linear
  systems: a relaxation strategy.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
  26(3):660--678, 2005.

\bibitem{BourasFraysseEtAl2000relaxation} A.~Bouras, V.~Frayssé, and L.~Giraud. \newblock A relaxation strategy
    for inner-outer linear solvers in domain
  decomposition methods.
\newblock {Technical Report} TR/PA/00/17, CERFACS, Toulouse, France, 2000.

\bibitem{BouyouliJbilouEtAl06Convergence} R.~Bouyouli, K.~Jbilou, R.~Sadaka, and H.~Sadok. \newblock Convergence
    properties of some block {K}rylov subspace methods for
  multiple linear systems.
\newblock {\em J. Comput. Appl. Math.}, 196(2):498--511, 2006.

\bibitem{BrezinaClearyEtAl2001Algebraic} M.~Brezina, A.~J. Cleary, R.~D. Falgout, V.~E. Henson, J.~E. Jones,
    T.~A.
  Manteuffel, S.~F. McCormick, and J.~W. Ruge.
\newblock Algebraic multigrid based on element interpolation ({AMGe}). \newblock {\em SIAM Journal on Scientific
Computing}, 22(5):1570--1592, 2001.

\bibitem{Brezinski2002Outils} C.~Brezinski. \newblock {\em Outils d'analyse numérique pour l'automatique},
    chapter
  Résolution des systèmes linéaires, pages 109--144.
\newblock Hermes Science Publications, 2002.

\bibitem{BrezinskiZaglia02Block} C.~Brezinski and M.~Redivo-Zaglia. \newblock Block projection methods for linear
    systems. \newblock {\em Numerical Algorithms}, 29(1-3):33--43, March 2002.

\bibitem{Broyden98Look-ahead} C.~Broyden. \newblock Look-ahead block-{CG} algorithm. \newblock In G.~W. Althaus
    and E.~Spedicato, editors, {\em Algorithms for Large
  Scale Linear Algebraic Systems}. Kluwer Academic,, 1998.

\bibitem{CalvezMolina1999Implicitly} C.~L. Calvez and B.~Molina. \newblock Implicitly restarted and deflated
    {GMRES}. \newblock {\em Numerical Algorithms}, 21:261--285, 1999.

\bibitem{Carvalho97Preconditioned} L.~M. Carvalho. \newblock {\em Preconditioned {S}chur complement methods in
    distributed memory
  environments}.
\newblock PhD thesis, INPT/CERFACS, France, Oct. 1997. \newblock TH/PA/97/41, CERFACS.

\bibitem{CarvalhoGiraudEtAl01Algebraic} L.~M. Carvalho, L.~Giraud, and P.~{L}e Tallec. \newblock Algebraic
    two-level preconditioners for the {S}chur complement
  method.
\newblock {\em SIAM J. Scientific Computing}, 22(6):1987--2005, 2001.

\bibitem{CarvalhoGiraudEtAl01Local} L.~M. Carvalho, L.~Giraud, and G.~Meurant. \newblock Local preconditioners for
    two-level nonoverlapping domain
  decomposition methods.
\newblock {\em Numerical Linear Algebra with Applications}, 8(4):207 -- 227,
  2001.

  \bibitem{CarvalhoGrattonEtAl2010Algebra} L.~M. Carvalho, S.~Gratton, R.~Lago, and N,~Maculan. \newblock Álgebra Linear Numérica e Computacional: Métodos de Krylov para a Solução de Sistemas Lineares.
\newblock {\em Livraria Ciência Moderna},   2010.


\bibitem{Chaitin-ChatelinFraysse1996Lectures} F.~{Chaitin-Chatelin} and V.~Frayssé. \newblock {\em Lectures on
    Finite Precision Computations}. \newblock SIAM, Philadelphia, 1996.

\bibitem{ChanVorst1997Parallel} T.~Chan and H.~van~der Vorst. \newblock {\em Parallel Numerical Algorithms,
    ICASE/LaRC Interdisciplinary
  Series in Science and Engineering}, chapter Approximate and incomplete
  factorizations, pages 167--202.
\newblock Kluwer, Dordrecht, 1997.

\bibitem{ChanWan97Analysis} T.~Chan and W.~Wan. \newblock Analysis of projection methods for solving linear
    systems with
  several right-hand sides.
\newblock {\em SIAM J. Sci. Comput.}, 18(6):1698--1721, 1997.

%\bibitem{Chan1987Rank} T.~F. Chan. \newblock Rank revealing {QR} factorizations. \newblock {\em Linear Algebra
%    Appl.}, 88/89:67--82, 1987.

%\bibitem{ChanHansen1992Some} T.~F. Chan and P.~C. Hansen. \newblock Some applications of the rank revealing {QR}
%    factorization. \newblock {\em SIAM Journal on Scientific and Statistical Computing},
%  13(3):727--741, 1992.

\bibitem{ChapmanSaad97Deflated} A.~Chapman and Y.~Saad. \newblock Deflated and augmented {K}rylov subspace
    techniques. \newblock {\em Numer. Linear Algebra Appli.}, 4(1):43--66, 1997.

\bibitem{Chen2005Matrix} K.~Chen. \newblock {\em Matrix Preconditioning Techniques and Applications}. \newblock
    Cambridge University Press, 2005.

\bibitem{ChowSaad97Approximate} E.~Chow and Y.~Saad. \newblock Approximate inverse techniques for
    block-partitioned matrices. \newblock {\em SIAM Journal on Scientific Computing}, 18(6):1657--1675, 1997.

\bibitem{ChowSaad98Approximatea} E.~Chow and Y.~Saad. \newblock Approximate inverse preconditioners via
    sparse-sparse iterations. \newblock {\em SIAM Journal on Scientific Computing}, 19(3):995--1023, 1998.

\bibitem{Cullum1996Iterative} J.~K. Cullum. \newblock Iterative methods for solving ${A}x=b$ {GMRES-FOM} versus
    {QMR/BiCG}. \newblock Technical Report TR-96-2, Institute for Advances Studies, University
  of Maryland, 1996.

\bibitem{CundyEshofEtAl2005Numerical} N.~Cundy, J.~van~den Eshof, A.~Frommer, S.~Krieg, T.~Lippert, and
    K.~Schafer. \newblock Numerical methods for the {QCD} overlap operator iii: Nested
  iterations.
\newblock {\em Comput. Phys. Comm.}, 165:221--242, 2005.

\bibitem{Sturler96Nested} E.~de~Sturler. \newblock Nested {{Krylov}} methods based on {GCR}. \newblock {\em J.
    Comput. Appl. Math.}, 67(1):15--41, 1996.

\bibitem{Sturler99Truncation} E.~de~Sturler. \newblock Truncation strategies for optimal {{Krylov}} subspace
    methods. \newblock {\em SIAM Journal on Numerical Analysis}, 36(3):864--889, 1999.

\bibitem{DrkovsovaRozlovznikEtAl1995Numerical} J.~Drko\v{s}ová, M.~Rozlo\v{z}ník, Z.~Strako\v{s}, and
    A.~Greenbaum. \newblock Numerical stability of the {GMRES} method. \newblock {\em BIT}, 35:309--330, 1995.

\bibitem{EiermannErnst01Geometric} M.~Eiermann and O.~G. Ernst. \newblock Geometric aspects of the theory of
    {K}rylov subspace methods. \newblock {\em Acta Numerica}, 10:251--312, 2001.

\bibitem{EiermannErnstEtAl00Analysis} M.~Eiermann, O.~G. Ernst, and O.~Schneider. \newblock Analysis of
    acceleration strategies for restarted minimal residual
  methods.
\newblock {\em Journal of Computational and Applied Mathematics}, 123:261--292,
  2000.

\bibitem{Embree1999How} M.~Embree. \newblock How descriptive are {GMRES} convergence bounds? \newblock Technical
    report, Oxford University Computing Laboratory, 1999.

\bibitem{ErhelBurrageEtAl96Restarted} J.~Erhel, K.~Burrage, and B.~Pohl. \newblock Restarted {GMRES}
    preconditioned by deflation. \newblock {\em Journal of Computational and Applied Mathematics},
  69(2,):303--318, May 1996.

\bibitem{FraysseGiraudEtAl2005set} V.~Frayssé, L.~Giraud, S.~Gratton, and J.~Langou. \newblock A set of {GMRES}
    routines for real and complex arithmetics on high
  performance computers.
\newblock {\em ACM Trans. Math. Softw.}, 31(2):228--238, 2005.

\bibitem{FreundMalhotra97Block} R.~Freund and M.~Malhotra. \newblock A block {QMR} algorithm for non-{Hermitian}
    linear systems with
  multiple right-hand sides.
\newblock {\em Linear Algebra and its Applications}, 254(1--3):119--157, 1997.


\bibitem{Gauss1995Theory} K. F.~Gauss. \newblock {\em Theory of the Combination of Observations Least Subject to Errors, Part One, Part Two, Supplement}. \newblock (Translated by G. W. Stewart) SIAM, 1995.

\bibitem{GeorgeLiu81Computer} A.~George and J.~Liu. \newblock {\em Computer solution of large sparse positive
    definite systems}. \newblock Computational Mathematics. Prentice-Hall, Englewood Cliffs, 1981.

\bibitem{GiraudGrattonEtAl07Convergence} L.~Giraud, S.~Gratton, and J.~Langou. \newblock Convergence in backward
    error of relaxed {GMRES}. \newblock {\em SIAM Journal on Scientific Computing}, 29(2):710--728, 2007.

\bibitem{GiraudGrattonEtAl2010Flexible} L.~Giraud, S.~Gratton, X.~Pinel, and X.~Vasseur. \newblock Flexible
    {GMRES} with deflated restarting. \newblock {\em SIAM J. Sci. Comput.}, 32(4):1858--1878, 2008.

\bibitem{GolubLoan96Matrix} G.~H. Golub and C.~F. van Loan. \newblock {\em Matrix Computations}. \newblock Johns
    Hopkins University Press, 3rd edition, 1996.

\bibitem{GolubYe1999Inexact} G.~H. Golub and Q.~Ye. \newblock Inexact preconditioned conjugate gradient method
    with inner-outer
  iteration.
\newblock {\em SIAM J. Sci. Comput.}, 21:1305--1320, 1999.

\bibitem{GoossensRoose99Ritz} S.~Goossens and D.~Roose. \newblock {Ritz} and harmonic {Ritz} values and the
    convergence of {FOM} and
  {GMRES}.
\newblock {\em Numerical linear algebra with applications}, 6(4):281--293,
  1999.

\bibitem{GouldScott95approximate-inverse} N.~Gould and J.~Scott. \newblock On approximate-inverse preconditioners.
    \newblock Technical Report RAL-95-026, Rutherford Appleton Laboratory, Chilton,
  1995.

\bibitem{Gratton2008Notes} S.~Gratton. \newblock Notes de cours. \newblock Unpublished lecture notes, 2008.

\bibitem{Greenbaum97Iterative} A.~Greenbaum. \newblock {\em Iterative Methods for Solving Linear Systems}.
    \newblock SIAM, Philadelphia, 1997.

\bibitem{GreenbaumPtakEtAl96Any} A.~Greenbaum, V.~Pták, and Z.~Strako{\u{s}}. \newblock Any nonincreasing
    convergence curve is possible for {GMRES}. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  17(3):465--469, July 1996.

\bibitem{GroteHuckle97Parallel} M.~J. Grote and T.~Huckle. \newblock Parallel preconditioning with sparse
    approximate inverses. \newblock {\em SIAM Journal on Scientific Computing}, 18(3):838--853, 1997.

\bibitem{GuWu99block} G.-D. Gu and H.-B. Wu. \newblock A block {EN} algorithm for nonsymmetric linear systems with
    multiple
  righ-hand sides.
\newblock {\em Linear Algebra and its Applications}, 299:1--20, 1999.

\bibitem{GuennouniJbilouEtAl03block} A.~E. Guennouni, K.~Jbilou, and H.~Sadok. \newblock A block version of
    {BICGSTAB} for linear systems with multiple
  right-hand sides.
\newblock {\em Electronic Transactions on Numerical Analysis}, 16(1):129--142,
  2003.

%\bibitem{Gutknecht2007Modern} M.~H. Gutknecht. \newblock {\em Modern Mathematical Models, Methods and Algorithms
%    for Real
%  World Systems}, chapter Block {Krylov} Space Methods for Linear Systems With
%  Multiple Right-hand Sides: an Introduction, pages 420--447.
%\newblock Anamaya Publishers, New Delhi, 2007.

\bibitem{Hackbusch1994Iterative} W.~Hackbusch. \newblock {\em Iterative Solution of Large Sparse Linear Systems of
    Equations}. \newblock Springer, 1994.

\bibitem{Higham02Accuracy} N.~J. Higham. \newblock {\em Accuracy and Stability of Numerical Algorithms}. \newblock
    SIAM, 2nd edition, 2002.

\bibitem{HoffmanKunze1971Linear} K.~Hoffman and R.~Kunze. \newblock {\em Linear Algebra}. \newblock Prentice-Hall,
    New Jersey, 2nd edition, 1971.

\bibitem{HornJohnson87Matrix} R.~A. Horn and C.~R. Johnson. \newblock {\em Matrix Analysis}. \newblock Cambridge
    University Press, 1987.

\bibitem{Householder1964Theory} A.~S. Householder. \newblock {\em Theory of Matrices in Numerical Analysis}.
    \newblock Dover, 1964.

\bibitem{Intel.comwww.intel.com} Intel. \newblock www.intel.com. \newblock visitado em 30 de março de 2008.

\bibitem{IpsenMeyer98Idea} I.~Ipsen and C.~Meyer. \newblock The idea behind {Krylov} methods. \newblock {\em Amer.
    Math. Monthly}, 105(10):889--899, 1998.

\bibitem{JiaStewart2001analysis} Z.~Jia and G.~W. Stewart. \newblock An analysis of the {Rayleigh-Ritz} method for
    approximating
  eigenspaces.
\newblock {\em Mathematics of Computation}, 70(234):637--647, 2001.

\bibitem{Joubert1994Robust} W.~Joubert. \newblock A robust {GMRES}-based adaptive polynomial preconditioning
    algorithm
  for nonsymmetric linear systems.
\newblock {\em SIAM Journal on Scientific Computing}, 15(2):427--439, 1994.

\bibitem{KantorovichKrylov1958Approximate} L.~V. Kantorovich and V.~I. Krylov. \newblock {\em Approximate methods
    of higher analysis}. \newblock John Wiley \& Sons, Inc., 1958.

\bibitem{Krylov1931numerical} A.~N. Krylov. \newblock On the numerical solution of the equation by which in
    technical
  questions frequencies of small oscillations of material systems are
  determined.
\newblock {\em News of Academy of Sciences of the USSR}, VII(4):491--539, 1931. \newblock (in Russian).

\bibitem{Lanczos1948Variational} C.~Lanczos. \newblock {\em The Variational Principles of Mechanics}. \newblock
    Number~4 in Mathematical Expositions. University of Toronto Press,
  Toronto, 1948.

\bibitem{Lang2003Algebra} S.~Lang. \newblock {\em Álgebra Linear}. \newblock Editora Ciencia Moderna, 2003.

\bibitem{Langou03Iterative} J.~Langou. \newblock {\em Iterative methods for solving linear systems with multiple
    right
  hand sides.}
\newblock {P}h.{D}. dissertation, INSA~Toulouse, June 2003. \newblock CERFACS-TH/PA/03/24.

\bibitem{Mathew2008Domain} T.~P.~A. Mathew. \newblock {\em Domain Decomposition Methods for the Numerical Solution
    of
  Partial Differential Equations}.
\newblock Springer, 2008.

\bibitem{Mer-NkongaCollino2002fast} K.~Mer-Nkonga and F.~Collino. \newblock The fast multipole method applied to a
    mixed integral system for
  time-harmonic {Maxwell's} equations.
\newblock In B.~Michielsen and F.~Decavèle, editors, {\em Proceedings of the
  European Symposium on Numerical Methods in Electromagnetics}, pages 121--126,
  Toulouse, France, 2002. ONERA.

\bibitem{Meurant1999Computer} G.~Meurant. \newblock {\em Computer solution of large linear systems}. \newblock
    North-Holland, 1999.

\bibitem{Meyer00Matrix} C.~D. Meyer. \newblock {\em Matrix analysis and applied liner algebra}. \newblock SIAM,
    2000.

\bibitem{Morgan1991Computing} R.~B. Morgan. \newblock Computing interior eigenvalues of large matrices. \newblock
    {\em Lin. Alg. and Its Applic.}, 154/156:289--309, 1991.

\bibitem{Morgan95Restarted} R.~B. Morgan. \newblock A restarted {GMRES} method augmented with eigenvectors.
    \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  16(4):1154--1171, 1995.

\bibitem{Morgan00Implicitly} R.~B. Morgan. \newblock Implicitly restarted {GMRES} and {Arnoldi} methods for
    nonsymmetric
  systems of equations.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
  21(4):1112--1135, 2000.

\bibitem{Morgan02GMRES} R.~B. Morgan. \newblock {GMRES} with deflated restarting. \newblock {\em SIAM Journal on
    Scientific Computing}, 24(1):20--37, 2002.

\bibitem{NachtigalReddyEtAl1992How} N.~M. Nachtigal, S.~C. Reddy, and L.~N. Trefethen. \newblock How fast are
    nonsymmetric matrix iterations? \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  13(3):778--795, 1992.

\bibitem{Nicolaides1987Deflation} R.~A. Nicolaides. \newblock Deflation of conjugate gradients with applications
    to boundary value
  problems.
\newblock {\em SIAM Journal on Numerical Analysis}, 24(2):355--365, 1987.

\bibitem{Notay00Flexible} Y.~Notay. \newblock Flexible conjugate gradients. \newblock {\em SIAM Journal on
    Scientific Computing}, 22(4):1444--1460, 2000.

\bibitem{OLeary80block} D.~O'Leary. \newblock The block conjugate gradient algorithm and related methods.
    \newblock {\em Linear Algebra and Its Applications}, 29:293--322, 1980.

\bibitem{PaigeParlettEtAl95Approximate} C.~C. Paige, B.~N. Parlett, and H.~A. van~der Vorst. \newblock Approximate
    solutions and eigenvalue bounds from {Krylov} subspaces. \newblock {\em Numerical Linear Algebra with
    Applications}, 2(2):115 -- 133,
  1995.

\bibitem{PaigeRozloznikEtAl2006MODIFIED} C.~C. Paige, M.~Rozlo{\u{z}}n{\'{\i}}k, and Z.~Strako{\u{s}}. \newblock
    Modified {G}ram-{S}chmidt ({MGS}), least squares, and backward
  stability of {MGS-GMRES}.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
  28(1):264--284, 2006.

\bibitem{ParksSturlerEtAl06Recycling} M.~L. Parks, E.~de~Sturler, G.~Mackey, D.~D. Johnson, and S.~Maiti.
    \newblock Recycling {Krylov} subspaces for sequences of linear systems. \newblock {\em SIAM Journal on
    Scientific Computing}, 28(5):1651--1674, 2006.

\bibitem{Parlett1998symmetric} B.~N. Parlett. \newblock {\em The symmetric eigenvalue problem}. \newblock SIAM,
    Philadelphia, 1998. \newblock Corrected reprint of the 1980 original.

\bibitem{QuarteroniSaccoEtAl2007Numerical} A.~Quarteroni, R.~Sacco, and F.~Saleri. \newblock {\em Numerical
    Mathematics}. \newblock Springer-Verlag, 2nd edition, 2007.

\bibitem{RobbeSadkane06Exact} M.~Robbé and M.~Sadkane. \newblock Exact and inexact breakdowns in the block {GMRES}
    method. \newblock {\em Linear Algebra and its Applications}, 419:265--285, 2006.

\bibitem{Rozloznik1997Numerical} M.~Rozlo\u{z}ník. \newblock {\em Numerical Stability of the GMRES Method}.
    \newblock PhD thesis, Institute of Computer Science, Academy of Sciences of the
  Czech Republic, Prague, April 1997.

\bibitem{RugeStuben1987Algebraic} J.~W. Ruge and K.~St{\"u}ben. \newblock {\em Multigrid Methods}, volume~3 of
    {\em Frontiers in Applied
  Mathematics}, chapter Algebraic multigrid ({AMG}), pages 73--130.
\newblock SIAM, Philadelphia, PA, 1987.

\bibitem{Saad1981Krylov} Y.~Saad. \newblock {Krylov} subspace methods for solving large unsymmetric linear
  systems.
\newblock {\em Math. Comp.}, 37(155):105--126, July 1981.

\bibitem{Saad93Flexible} Y.~Saad. \newblock A flexible inner-outer preconditioned {GMRES} algorithm. \newblock
    {\em SIAM Journal on Scientific Computing}, 14(2):461--469, 1993.

\bibitem{Saad97Analysis} Y.~Saad. \newblock Analysis of augmented {Krylov} subspace methods. \newblock {\em SIAM
    Journal on Matrix Analysis and Applications},
  18(2):435--449, 1997.

\bibitem{Saad03Iterative} Y.~Saad. \newblock {\em Iterative Methods for Sparse Linear Systems}. \newblock SIAM,
    2nd edition, 2003.

\bibitem{SaadSchultz86GMRES} Y.~Saad and M.~H. Schultz. \newblock {GMRES}: a generalized minimal residual
    algorithm for solving
  nonsymmetric linear systems.
\newblock {\em SIAM J. Sci. Stat. Comput.}, 7(3):856--869, 1986.

\bibitem{SaadVorst00Iterative} Y.~Saad and H.~A. van~der Vorst. \newblock Iterative solution of linear systems in
    the 20th century. \newblock {\em Journal of Computational and Applied Mathematics},
  123(1-2):1--23, 2000.

\bibitem{SaadYeungEtAl00Deflated} Y.~Saad, M.~Yeung, J.~Erhel, and F.~Guyomarc'h. \newblock A deflated version of
    the conjugate gradient algorithm. \newblock {\em SIAM Journal on Scientific Computing}, 21(5):1909--1926,
    2000.

\bibitem{SalaHerouxEtAl04Trilinos} M.~Sala, M.~A. Heroux, and D.~M. Day. \newblock {Trilinos Tutorial}. \newblock
    Technical Report SAND2004-2189, Sandia National Laboratories, 2004.

%\bibitem{Schmelzer2004Block} T.~Schmelzer. \newblock Block {Krylov} methods for {Hermitian} linear systems.
%    \newblock Diploma thesis, Department of Mathematics, University of
%  Kaiserslautern, Germany, 2004.

\bibitem{Schwarz90Uber} H.~Schwarz. \newblock {\"{U}}ber eine grenz{\"{u}}bergang durch alternirendes verfahren.
    \newblock {\em Gesammelete Mathematische Abhandlungen, Springer-Verlag},
  2:133--143, 1890.
\newblock First published in Vierteljahrsschrift der Naturforschenden
  Gesellschaft in Z{\"{u}}rich, vol.15, pp. 272-286, 1870.

\bibitem{Scott1982Advantages} D.~S. Scott. \newblock The advantages of inverted operators in {Rayleigh--Ritz}
  approximations.
\newblock {\em SIAM Journal on Scientific and Statistical Computing},
  3(1):68--75, 1982.

\bibitem{Shewchuk94Introduction} J.~R. Shewchuk. \newblock An introduction to the conjugate gradient method
    without the
  agonizing pain edition 1$\frac{1}{4}$.
\newblock Technical report, School of Computer Science, Carnegie Mellon
  University, August 1994.

\bibitem{Simoncini97Stabilized} V.~Simoncini. \newblock A stabilized {QMR} version of block {BiCG}. \newblock {\em
    SIAM Journal on Matrix Analysis and Applications},
  18(2):419--434, 1997.

\bibitem{Simoncini00Convergence} V.~Simoncini. \newblock On the convergence of restarted {Krylov} subspace
    methods. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  22(2):430--452, 2000.

\bibitem{SimonciniSzyld02Flexible} V.~Simoncini and D.~B. Szyld. \newblock Flexible inner-outer {Krylov} subspace
    methods. \newblock {\em SIAM Journal on Numerical Analysis}, 40(6):2219--2239, 2002.

\bibitem{SimonciniSzyld03Theory} V.~Simoncini and D.~B. Szyld. \newblock Theory of inexact {Krylov} subspace
    methods and applications to
  scientific computing.
\newblock {\em SIAM Journal on Scientific Computing}, 25(2):454--477, 2003.

\bibitem{SimonciniSzyld2005effect} V.~Simoncini and D.~B. Szyld. \newblock The effect of non-optimal bases on the
    convergence of {Krylov}
  subspace methods.
\newblock {\em Numerische Mathematik}, 100(4):711--733, June 2005.

\bibitem{SimonciniSzyld2007Recent} V.~Simoncini and D.~B. Szyld. \newblock Recent computational developments in
    {Krylov} subspace methods for
  linear systems.
\newblock {\em Numerical Linear Algebra with Applications}, 14:1 -- 59, 2007.

\bibitem{SleijpenEshof2003use} G.~L.~G. Sleijpen and J.~van~den Eshof. \newblock On the use of harmonic {Ritz}
    pairs in approximating internal
  eigenpairs.
\newblock {\em Linear Algebra and its Applications}, 358(1-3):115--137, January
  2003.

\bibitem{SleijpenVorst00JacobiDavidson} G.~L.~G. Sleijpen and H.~A. van~der Vorst. \newblock A {Jacobi--Davidson}
    iteration method for linear eigenvalue problems. \newblock {\em SIAM Review}, 42(2):267--293, 2000. \newblock
    This paper originally appeared in SIAM Journal on Matrix Analysis and
  Applications, Volume 17, Number 2, 1996, pages 401-425.

\bibitem{SmithEtAl96Domain} B.~Smith, P.~Bj{\o}rstad, and W.~Gropp. \newblock {\em {D}omain {D}ecomposition,
    {P}arallel {M}ultilevel {M}ethods for
  {E}lliptic {P}artial {D}ifferential {E}quations}.
\newblock Cambridge University Press, New York, 1st edition, 1996.

\bibitem{Stewart1973Introduction} G.~W. Stewart. \newblock {\em Introduction to Matrix Computations}. \newblock
    Academic Press, New York, 1973.

\bibitem{Stewart98Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume I}: Basic Algorithms}.
    \newblock SIAM, Philadelphia, PA, USA, 1998.

\bibitem{Stewart01Matrix} G.~W. Stewart. \newblock {\em Matrix Algorithms. {Volume II}: Eigensystems}. \newblock
    SIAM, 2001.

\bibitem{StewartSun1990Matrix} G.~W. Stewart and J.~Sun. \newblock {\em Matrix Perturbation Theory}. \newblock
    Academic Press, 1990.

\bibitem{Strang1988Linear} G.~Strang. \newblock {\em Linear Algebra and Its Applications}. \newblock Harcourt
    Brace Jovanovich, Publishers, San Diego, 1988.

\bibitem{SzyldVogel01FQMR} D.~B. Szyld and J.~A. Vogel. \newblock {FQMR}: A flexible quasi-minimal residual method
    with inexact
  preconditioning.
\newblock {\em SIAM Journal on Scientific Computing}, 23(2):363--380, 2001.

\bibitem{The04Matlab} {The Mathworks, {Inc}}. \newblock {\em Matlab 7.0}, 2004.

\bibitem{ToselliWidlund2004Domain} A.~Toselli and O.~Widlund. \newblock {\em Domain Decomposition methods -
    Algorithms and Theory}, volume~34
  of {\em Computational Mathematics}.
\newblock Springer, 2004.

\bibitem{Trefethen1990Algorithms} L.~N. Trefethen. \newblock {\em Algorithms for Approximation II}, chapter
    Approximation theory
  and numerical linear algebra, pages 336--360.
\newblock Chapman and Hall, London, 1990.

\bibitem{TrefethenBau97Numerical} L.~N. Trefethen and D.~{Bau, III}. \newblock {\em Numerical linear algebra}.
    \newblock SIAM, 1997.

\bibitem{TrottenbergOosterleeEtAl2001Multigrid} U.~Trottenberg, C.~Oosterlee, and A.~Schuller. \newblock {\em
    Multigrid}. \newblock Academic Press, 2001.

\bibitem{EshofSleijpen04Inexact} J.~van~den Eshof and G.~L.~G. Sleijpen. \newblock Inexact {Krylov} subspace
    methods for linear systems. \newblock {\em SIAM Journal on Matrix Analysis and Applications},
  26(1):125--153, 2004.

\bibitem{EshofSleijpenEtAl2005Relaxation} J.~van~den Eshof, G.~L.~G. Sleijpen, and M.~B. van Gijzen. \newblock
    Relaxation strategies for nested {Krylov} methods. \newblock {\em J. Comput. Appl. Math.}, 177:347--365,
    2005.

\bibitem{Vorst03Iterative} H.~van~der Vorst. \newblock {\em Iterative {Krylov} Methods for Large Linear systems}.
    \newblock Cambridge University Press, Cambridge, April 2003.

\bibitem{VorstVuik94GMRESR} H.~van~der Vorst and C.~Vuik. \newblock {GMRESR}: a family of nested {GMRES} methods.
    \newblock {\em Numerical Linear Algebra with Applications}, 4(1):369--386,
  1994.

\bibitem{VorstVuik1993superlinear} H.~A. van~der Vorst and C.~Vuik. \newblock The superlinear convergence
    behaviour of {GMRES}. \newblock {\em J. Comput. Appl. Math.}, 48:327--341, 1993.

\bibitem{Vuik1995New} C.~Vuik. \newblock New insights in {GMRES-like} methods with variable preconditioners.
    \newblock {\em J. Comput. Appl. Math.}, 61:189--204, 1995.

\bibitem{WarsaBenziEtAl2004Preconditioning} J.~S. Warsa, M.~Benzi, T.~A. Warein, and J.~E. Morel. \newblock
    Preconditioning a mixed continuous finite element method for
  radiation diffusion.
\newblock {\em Numerical Lin. Alg. and Its Applic.}, 11:795--811, 2004.

\bibitem{Wesseling92Introduction} P.~Wesseling. \newblock {\em An Introduction to Multigrid Methods}. \newblock
    Wiley, New York, 1992.

\bibitem{WesselingOosterlee2001Geometric} P.~Wesseling and C.~Oosterlee. \newblock Geometric multigrid with
    applications to computational fluid
  dynamics.
\newblock {\em Journal of Computational and Applied Mathematics},
  128(1-2):311--334, 2001.

\bibitem{Wilkinson63Rounding} J.~H. Wilkinson. \newblock {\em Rounding Errors in Algebraic Processes}. \newblock
    Notes on Applied Science No. 32, Her Majesty's Stationery Office,
  London, 1963.
\newblock Also published by Prentice-Hall, Englewood Cliffs, NJ, USA. Reprinted
  by Dover, New York, 1994.

\bibitem{WuSimon2000Thick-Restart} K.~Wu and H.~Simon. \newblock Thick-restart {Lanczos} method for large
    symmetric eigenvalue
  problems.
\newblock {\em SIAM Journal on Matrix Analysis and Applications},
  22(2):602--616, 2000.

\bibitem{YuSturlerEtAlblock} R.~Yu, E.~de~Sturler, and D.~D. Johnson. \newblock A block iterative solver for
    complex non-{H}ermitian systems applied
  to large-scale, electronic-structure calculations.
\newblock 1999.

\bibitem{Zemke2003Krylov} J.-P.~M. Zemke. \newblock {\em {Krylov} Subspace Methods in Finite Precision: A Unified
  Approach}.
\newblock PhD thesis, Technischen Universität Hamburg-Harburg, 2003.

\bibitem{Zhang00Sparse} J.~Zhang. \newblock Sparse approximate inverse and multilevel block {ILU} preconditioning
  techniques for general sparse matrices.
\newblock {\em Applied Numerical Mathematics}, 35(1):67--86, Sept. 2000.

\markboth{}{}

\end{thebibliography}

